kNN Implementation

### 2020-10-06 DATA622/M05-kNN.rmd
Updated KNN files

knn.df<-catheart
labelcol <- 9 # for iris it is the fifth col 
predictioncol<-labelcol+1
# create train/test partitions
set.seed(43)
n<-nrow(knn.df)
knn.df<- knn.df[sample(n),] # randomize

@@

```{r}
start_time <- Sys.time()
n_tests <- 100
for (i in 1:n_tests){
  knn_predict2(test.df, train.df, K,labelcol)
}
end_time <- Sys.time()
difftime(end_time, start_time)
```

```{r}
start_time <- Sys.time()
for (i in 1:n_tests){
  knn_predict3(test.df, train.df, K,labelcol)
}
end_time <- Sys.time()
difftime(end_time, start_time)
```
Computing ROCR and AUC is some what non-trivial as kNN do not compute probabilities
and results in unreliable ROCR plots.
```{r}
test.df[,predictioncol] <- predictions #
print(paste('accuracy=',accuracy(test.df,labelcol,predictioncol)))
```
Now let us label the test set using standard kNN implementation from class
package.
```{r}
library(class)
library(ROCR)

>>>>

knn.df<-catheart
labelcol <- 9 # for iris it is the fifth col 
predictioncol<-labelcol+1
# create train/test partitions
set.seed(43)
n<-nrow(knn.df)
index <- sample(n)
knn.df<- knn.df[index,] # randomize

@@

```{r}
# start_time <- Sys.time()
# n_tests <- 100
# for (i in 1:n_tests){
#   knn_predict2(test.df, train.df, K,labelcol)
# }
# end_time <- Sys.time()
# difftime(end_time, start_time)
```

```{r}
# start_time <- Sys.time()
# for (i in 1:n_tests){
#   knn_predict3(test.df, train.df, K,labelcol)
# }
# end_time <- Sys.time()
# difftime(end_time, start_time)
```
Computing ROCR and AUC is some what non-trivial as kNN do not compute probabilities
and results in unreliable ROCR plots.
```{r}
test.df[,predictioncol] <- predictions #
print(paste('accuracy=',accuracy(test.df,labelcol,predictioncol)))
```
Now let us label the test set using standard kNN implementation from class
package.
```{r}
library(class)
library(ROCR)
